---
title: ""
format: 
  html:
    theme: journal
    css: custom.css
editor: visual
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---

```{r}
#| include: false
#| cache: false
googlesheets4::gs4_deauth()
cv_url <- "https://docs.google.com/spreadsheets/d/1_OLB0r_0boMLlCY_0qdS48KsCTmOpTeKKeiLPleVDTA/edit#gid=1060177346"
cv <- googlesheets4::read_sheet(cv_url)
```

<!-- Sidebar -->

::: columns
::: {.column .aside width="25%"}
<center>

<a href='https://ambarja.github.io' target='_blank'> ![](https://avatars.githubusercontent.com/u/23284899?v=4){width="80%" style="border-radius: 50%;"}

</center>

</a>

### Contact

<center>

<span style="font-size: 1.5em;"> <a href='https://ambarja.github.io' target='_blank'><i class="fa fa-home"></i></a> <a href='https://github.com/ambarja' target='_blank'><i class="fa-brands fa-github"></i></a> <a href='mailto:antonymarcosbarja@gmail.com'><i class="fa fa-envelope"></i></a> <a href='https://twitter.com/antony_barja' target='_blank'><i class="fa-brands fa-twitter"></i></a> <a href='' target='_blank'><i class="fab fa-discord"></i></a>

</center>

</span>

Hello! I am a spatial data scientist in development in the [**Healthinnovation Lab**](https://www.innovalab.info/) at the Universidad Peruana Cayetano Heredia - Peru. 
I am currently a GIS analyst and developer.
My work environment involves spatial data analysis and spatio-temporal modeling with focus on spatial epidemiology.
My main skills are the use of different free and open source geographic information technologies.


### Languages

**Spanish:** Native <br> **English:** Learning

### Software

<i class="fas fa-box-open"></i> [Package {rgee} - Available on CRAN](https://r-spatial.github.io/rgee/) - Co-Author.

<i class="fas fa-box-open"></i> [Package {innovar}](https://healthinnovation.github.io/innovar/) - Author, maintainer.

### Skills

<i class="fa-solid fa-q"></i> `QGIS` <br> <i class="fab fa-r-project"></i> `R` <br> <i class="fa-brands fa-google"></i> `EarthEngine` <br> <i class="fa-solid fa-terminal"></i> `Bash` <br> <i class="fa-solid fa-database"></i> `PostgreSQL` <br> <i class="fa-brands fa-linux"></i> `Linux` <br> <i class="fa-brands fa-python"></i>`python` <br> <i class="fab fa-html5"></i> `HTML` <br> <i class="fab fa-css3-alt"></i> `CSS` <br> <i class="fa-brands fa-js"></i> `Js` <br> <i class="fab fa-markdown"></i> `Markdown` <br> <i class="fas fa-code-branch"></i> `Git` <br> <i class="fab fa-github"></i> `GitHub` <br>
:::

::: {.column width="5%"}
:::

::: {.column width="70%"}
<!-- Functions -->

```{r}
col_br <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0(col, ""),
      ""
    )
}

col_br_loc <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0('<i class="fa-solid fa-location-dot"></i> ', col),
      ""
    )
}

create_section <- function(cv_data, section_name){
  cv_data |>
    dplyr::mutate(in_resume = as.character(in_resume),
                  end = tidyr::replace_na(end, 9999),
                  loc = dplyr::if_else(loc == "Online", NA_character_, loc)) |>
    dplyr::filter(in_resume %in% c("TRUE", "VERDADEIRO"), section == section_name) |>
    dplyr::select(section:description_1) |>
    dplyr::arrange(desc(end), desc(start)) |>
    dplyr::mutate(
      date =
        dplyr::case_when(
          end == 9999 ~ glue::glue("Current <br> | <br> {start}"),
          end != start ~ glue::glue("{end} <br> | <br> {start}"),
          end == start ~ glue::glue("{end}"),
          TRUE ~ ""
        ) ,
      .before = everything()
    ) |>
    dplyr::mutate(
      main_text =
        glue::glue(
          "**{title}** <br> {col_br(institution)} {col_br(description_1)} {col_br_loc(loc)}"),
      .after = date
    ) |>
    dplyr::select(-c(start, end, section, title, institution, loc, description_1)) |>
    gt::gt() |>
    gt::fmt_markdown(columns = c(date, main_text)) |> 
    gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100)) |> 
    gt::cols_align(align = "left", columns = main_text)
}
```

<!-- Main content -->

# Antony Barja

## <i class="fa-solid fa-suitcase"></i> Work

```{r}
create_section(cv, "working_experience")
```

## <i class="fa-solid fa-chalkboard-user"></i> Selected talks

```{r}
create_section(cv, "oral_communications")
```

## <i class="fa-solid fa-graduation-cap"></i> Education

```{r}
create_section(cv, "education")
```
:::
:::

<!-- footer -->

<p class="footer">

Resume made with 💜 and [Quarto](https://quarto.org/). Last updated on `r format.Date(Sys.Date(), "%b %d, %Y")`. <br> Code available on <i class="fa-brands fa-github"></i> [GitHub](https://github.com/ambarja/Resume). <br>License: [CC BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/).

</p>

```{=html}
<script src="https://kit.fontawesome.com/1bb720cc6f.js" crossorigin="anonymous"></script>
```
